State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-24 paper/chapters/1_introduction.tex
Typos

% steps
In general sentiment analysis can be splitted into two steps: a preprocessing and a constitutive sentiment analysis phase. In Twitter sentiment analysis there is another step right bevor preprocessing: fetching the data from the application programming interface (API). This task is not trivial, because the official API is limited regarding the datasets fetched within certain intervals. This leads to the requirement of a caching mechanism to avoid fetching the same tweets multiple times and allow the usage of more datasets.

@@

\section{Related Work}
Sentiment analysis a growing and well explored part of Natural Language Processing (NLP). There are several papers from \citeauthor{Pang2008} regarding sentiment analysis in general and related topics like the effects of various machine learning approaches \autocite{Pang2002}\autocite{Pang2008}. Especially the last topic is a well studied field \autocite{Manning2000}.
Some related research areas are document level classification, sentence-level classification and machine learning. Due the limited number of characters within a single twitter post, this topic is quite similar to sentence-level sentiment analysis.
There are several recent papers regarding sentiment analysis in the context of twitter posts. \citeauthor{Agarwal2011} published within \citetitle{Agarwal2011} general information and techniques which cover this area \autocite{Agarwal2011}. In \citetitle{Kouloumpis2011} the utility of linguistic features for detecting the sentiment of tweets are investigated. 
\citeauthor{Saif2012} introduce a novel approach of adding semantics as additional features into the training set. For each extracted entity (e.g. Galaxy S) from Twitter Messages, they add a semantic concept (e.g. Samsung product) as an additional feature, and measure the correlation of the representative concept with negative/positive sentiment \autocite{Saif2012}. In \citetitle{Go2009} a algorithm is presented, which accurately classifies tweets as positive or negative, in respect to a query term\autocite{Go2009}.

>>>>

% steps
In general, sentiment analysis can be splitted into two steps: a preprocessing and a constitutive sentiment analysis phase. In Twitter sentiment analysis there is another step right before preprocessing: fetching the data from the application programming interface (API). This task is not trivial, because the official API is limited regarding the datasets fetched within certain intervals. This leads to the requirement of a caching mechanism to avoid fetching the same tweets multiple times and allow the usage of more datasets.

@@

\section{Related Work}
Sentiment analysis a growing and well explored part of Natural Language Processing (NLP). There are several papers from \citeauthor{Pang2008} regarding sentiment analysis in general and related topics like the effects of various machine learning approaches \autocite{Pang2002}\autocite{Pang2008}. Especially the last topic is a well studied field \autocite{Manning2000}.
Some related research areas are document level classification, sentence-level classification and machine learning. Due the limited number of characters within a single twitter post, this topic is quite similar to sentence-level sentiment analysis.
There are several recent papers regarding sentiment analysis in the context of twitter posts. \citeauthor{Agarwal2011} published within \citetitle{Agarwal2011} general information and techniques which cover this area \autocite{Agarwal2011}. In \citetitle{Kouloumpis2011} the utility of linguistic features for detecting the sentiment of tweets are investigated. 
\citeauthor{Saif2012} introduce a novel approach of adding semantics as additional features into the training set. For each extracted entity (e.g. Galaxy S) from Twitter Messages, they add a semantic concept (e.g. Samsung product) as an additional feature, and measure the correlation of the representative concept with negative/positive sentiment \autocite{Saif2012}. In \citetitle{Go2009}, an algorithm is presented, which accurately classifies tweets as positive or negative in respect to a query term\autocite{Go2009}.

### 2015-01-24 paper/chapters/3_preprocessing.tex
Typos

\subsection{Tagger}
Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefor
very useful for Natural Language Processing.
Tagging Tweets is very challenging, because of the twitter specific slang, emoticons and the lack of conventional orthography.
%TODO: Quelle: Part-of-Speech Tagging for Twitter: Annotation, Features, and Experiments
There is a variety of freely downloadable POS taggers
\footnote{http://www-nlp.stanford.edu/links/statnlp.html} e.g. Stanford POS tagger
\footnote{http://nlp.stanford.edu/software/tagger.shtml}
 but just a few are specialized on tagging twitter data like the TweetNLP tagger
\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}. In comparison with the Stanford POS tagger the TweetNLP tagger
 reduces errors by 25\%.
 %TODO Quelle: http://iswc2012.semanticweb.org/sites/default/files/76490497.pdf

>>>>

\subsection{Tagger}
Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefore
very useful for Natural Language Processing.
Tagging Tweets is very challenging, because of the twitter specific slang, emoticons and the lack of conventional orthography.
%TODO: Quelle: Part-of-Speech Tagging for Twitter: Annotation, Features, and Experiments
spelling errors, bad structure, abbreviations, and slang
%TODO Quelle: Mirroring the Real World in Social Media: Twitter, Geolocation, and Sentiment Analysis
There is a variety of freely downloadable POS taggers
\footnote{http://www-nlp.stanford.edu/links/statnlp.html} e.g. Stanford POS tagger
\footnote{http://nlp.stanford.edu/software/tagger.shtml}
 but just a few are specialized on tagging twitter data like the TweetNLP tagger
\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}. In comparison with the Stanford POS tagger the TweetNLP tagger
 reduces errors by 25\%.
 %TODO Quelle: http://iswc2012.semanticweb.org/sites/default/files/76490497.pdf
